Viscous Transport in Eroding Porous Media

### 2019-05-24 docs/transport/erosion_transport.tex
add tracer figure of 100 bodies in transport paper
add definition of porosity in transport paper
add tortuousity figures in transport paper
add a tortuousity figure in transport paper
small changes addressing S-H's email
redo the result section in transport paper

We will be using quadrature formulae to compute $v$ and its derivatives
that rely on the Cauchy integral theorem.  Since $v$ is holomorphic, its
value only depends on its boundary data.  The boundary data satisfies
the Sokhotski-Plemelj jump relation
\begin{align}
  \label{eqn:SPrelation}
  v(x) = -\frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
\end{align}
Once the boundary data of $v$ is computed, we have
\begin{align}
  \label{eqn:cauchy}
  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \quad
  v'(x) = -\frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \quad
  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy.
\end{align}
for $x \in \Omega$.  Since $v(x)$ depends on the density function $\eta
\in \CC$, we use the notation $v[\eta](x)$ to denote the holomorphic
function defined in equation~\eqref{eqn:laplaceComplex}, and the
derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.

@@

@@

Consider eroding bodies $\gamma_k$, $k=1,\ldots,M$, in a fluid domain
$\Omega$ with boundary $\Gamma$.  Let the length of $\Gamma$ be $L_{0}$,
and the length of $\gamma_k$ be $L_k$.  We discretize each eroding body
$\gamma_k$ with $N_\iin$ points and discretize $\Gamma$ with $N_\out$
points.  The $j^{th}$ discretization point on $\Gamma$ is denoted by
$\yy_j^0$, and the $j^{th}$ discretization point on $\gamma_k$ is
denoted by $\yy^k_j$.  The discretization points are initially
distributed evenly in arclength, and this equispacing is maintained for
the entire simulation by using a {\thL}
formulation~\cite{hou-low-she1994}.  In addition, we apply mild
smoothing strategies~\cite{qua-moo2018} to avoid the corners that
erosion inevitably develop.    Since the points are equispaced, the
trapezoid rule to evaluate the velocity at a target point $\xx$ is
\begin{align}
  \label{eqn:trap}
  \uu(\xx) \approx \frac{L_0}{N_\out} \sum_{j=1}^{N_\out} 
    D(\xx,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \sum_{j=1}^{N_\iin}
    D(\xx,\yy^k_j) \eeta^k_j,
\end{align}
where $D$ is the kernel of the Stokes double-layer potential defined in
Equation~\eqref{eqn:stokesDLP}.

@@

At each GMRES iteration, we must compute the velocity at each
discretization point on $\bd\Omega$.  To reduce the cost of computing
the velocity, we start by using the trapezoid rule~\eqref{eqn:trap}
accelerated with the fast multipole method (FMM)~\cite{gre-rok1987},
which requires $\mathcal{O}(N)$ operations, and we call this velocity
$v_\trap(\xx)$.  For target points that are sufficiently far from
$\bd\Omega$, $v_\trap(\xx)$ is sufficiently accurate.  However, this
velocity is inaccurate at points that are too close to $\bd\Omega$, and
the velocity must be corrected.  Assuming that $\xx$ is too close to
$\gamma_k$, only the velocity due to $\gamma_k$ must be corrected. We
first subtract the velocity contribution of $\vv(\xx)$ due to
$\gamma_k$.  Then, the Barycentric quadrature rule is used to compute
the velocity due to $\gamma_i$ with more accuracy.  That is, the
final velocity is
\begin{align}
  \vv(\xx) = \vv_\trap(\xx) - \frac{L_k}{N_k} \sum_{j=1}^{N_\iin} 
    D(\xx,\yy^k_j) \eeta(\yy_j) + v^k_\bary(\xx),
\end{align}
where $v^k_\bary(\xx)$ is the velocity at $\xx$ resulting from applying
the Barycentric quadrature rule due to $\gamma_k$.  This method
naturally extends to points that are close to $\Gamma$, and to the
scenario when $\xx$ is simultaneously close to multiple components of
$\bd\Omega$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the shear stress on the body. In this simulation, we use three minimum body-to-wall initial distances $d=h$(left), $h/2$(middle), and $h/10$(right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt$, and smoothing parameters of $\eps $ and $\sigma $.}
\label{} 
\end{center}
\end{figure}
{\color{red} We first consider a single circular body in a shear flow. 
The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. 
The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$. 
Let the initial radius of the body be $r$, 
the initial length of the body be $L$, $N_\iin$ and 
$N_\out$ be the number of discretization points 
on the body and wall respectively, 
$h=L/N_\iin$ be the resolution mesh size of the body, 
and $d$ be the minimum initial distance from body to wall. 
To investigate the shape of eroding body when it is close to wall, 
we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ 
with respect to three different $d=h, h/2$, and $ h/10$.

@@

\begin{figure}[H]
\begin{center}
\caption{The tortuosity of the 20 nearly touching bodies}
\end{center}
\end{figure}

@@

\subsection{100 bodies}
{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow.
}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the fixed-pressure-drop condition. The color is the vorticity of fluid. In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{s:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

We will be using quadrature formulae to compute $v$ and its derivatives
that rely on the Cauchy integral theorem.  Since $v$ is holomorphic, its
value only depends on its boundary data.  The boundary data satisfies
the Sokhotski-Plemelj jump relation
\begin{align}
  \label{eqn:SPrelation}
  v(x) = -\frac{1}{2} \eta(x) + \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{\eta(y)}{x-y}\, dy, \quad x \in \bd\Omega.
\end{align}
Once the boundary data of $v$ is computed, we have
\begin{align}
  \label{eqn:cauchy}
  v(x) = \frac{1}{2\pi i}\int_{\bd\Omega} 
    \frac{v(y)}{y-x} \,dy, \quad
  v'(x) = \frac{1}{2\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^2} \, dy, \quad
  v''(x) = \frac{1}{\pi i} \int_{\bd\Omega}
    \frac{v(y)}{(y-x)^3} \, dy.
\end{align}
for $x \in \Omega$.  Since $v(x)$ depends on the density function $\eta
\in \CC$, we use the notation $v[\eta](x)$ to denote the holomorphic
function defined in equation~\eqref{eqn:laplaceComplex}, and the
derivatives are written as $v'[\eta](x)$ and $v''[\eta](x)$.

@@

{\color{red} the definition of porosity is the ratio 
$$\phi=\frac{A_v}{A_T}$$
where $A_v$ is the area of void-space and $A_T$ is the area of the calculating area.
}

@@

Consider eroding bodies $\gamma_k$, $k=1,\ldots,M$, in a fluid domain
$\Omega$ with boundary $\Gamma$.  Let the length of $\Gamma$ be $L_{0}$,
and the length of $\gamma_k$ be $L_k$.  We discretize each eroding body
$\gamma_k$ with $N_\iin$ points and discretize $\Gamma$ with $N_\out$
points.  The $j^{th}$ discretization point on $\Gamma$ is denoted by
$\yy_j^0$, and the $j^{th}$ discretization point on $\gamma_k$ is
denoted by $\yy^k_j$.  The discretization points are initially
distributed evenly in arclength, and this equispacing is maintained for
the entire simulation by using a {\thL}
formulation~\cite{hou-low-she1994}.  In addition, we apply mild
smoothing strategies~\cite{qua-moo2018} to avoid the corners that
erosion inevitably develop.    Since the points are equispaced, the
trapezoid rule to evaluate the velocity at a target point $\xx$ is
\begin{align}
  \label{eqn:trap}
  \uu(\xx) \approx \frac{L_0}{N_\out} \sum_{j=1}^{N_\out} 
    D(\xx,\yy^0_j) \eeta_j +
  \sum_{k=1}^M \frac{L_k}{N_\iin} \sum_{j=1}^{N_\iin}
    D(\xx,\yy^k_j) \eeta^k_j,
\end{align}
where $D$ is the kernel of the Stokes double-layer potential defined in
Equation~\eqref{eqn:stokesDLP}.

@@

At each GMRES iteration, we must compute the velocity at each
discretization point on $\bd\Omega$.  To reduce the cost of computing
the velocity, we start by using the trapezoid rule~\eqref{eqn:trap}
accelerated with the fast multipole method (FMM)~\cite{gre-rok1987},
which requires $\mathcal{O}(N)$ operations, and we call this velocity
$v_\trap(\xx)$.  For target points that are sufficiently far from
$\bd\Omega$, $v_\trap(\xx)$ is sufficiently accurate.  However, this
velocity is inaccurate at points that are too close to $\bd\Omega$, and
the velocity must be corrected.  Assuming that $\xx$ is too close to
$\gamma_k$, only the velocity due to $\gamma_k$ must be corrected. We
first subtract the velocity contribution of $\vv(\xx)$ due to
$\gamma_k$.  Then, the Barycentric quadrature rule is used to compute
the velocity due to $\gamma_i$ with more accuracy.  That is, the
final velocity is
\begin{align}
  \vv(\xx) = \vv_\trap(\xx) - \frac{L_k}{N_k} \sum_{j=1}^{N_\iin} 
    D(\xx,\yy^k_j) \eeta(\yy_j) + \vv^k_\bary(\xx),
\end{align}
where $v^k_\bary(\xx)$ is the velocity at $\xx$ resulting from applying
the Barycentric quadrature rule due to $\gamma_k$.  This method
naturally extends to points that are close to $\Gamma$, and to the
scenario when $\xx$ is simultaneously close to multiple components of
$\bd\Omega$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Results}
\label{s:results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We do some simulations.  The parameters are
\begin{itemize}
  \item time step size
  \item regularization and smoothing parameters
  \item resolution on bodies and solid wall
\end{itemize}
{\color{red} In this section, we present the numerical simulations of bodies eroding in the fluid. The computational domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded off corners and we place bodies only in $[-1,1]\times[-1,1]$. We impose the fixed-pressure-drop condition on the simulation
 smoothing parameters of $\eps$ and $\sigma $.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{A single body close to a wall}
\todo[inline]{Do a single body that is extremely close one of the two
horizontal walls.  This can be compared to some of the
results~\cite{mit-spa2017}.  Do for a variety of distances to
demonstrate how close we can put it to the wall with no need to increase
the resolution}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r1h_shear}
\includegraphics[width = 0.30 \textwidth]{./figs/1b_0d4r0d5h_shear}
\includegraphics[width = 0.35 \textwidth]{./figs/1b_0d4r0d1h_shear}
\caption{A single body eroding in Stokes flow. Color indicates the shear stress on the body. In this simulation, we use three minimum body-to-wall initial distances $d=h$ (left), $h/2$ (middle), and $h/10$ (right) with $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=0.0001$, and smoothing parameters of $\eps$ and $\sigma $.}
\label{} 
\end{center}
\end{figure}
{\color{red} We first consider a single circular body in a shear flow. 
The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. 
The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=x_2+1$. 
Let the initial radius of the body be $r$, 
the initial length of the body be $L$, $N_\iin$ and 
$N_\out$ be the number of discretization points 
on the body and wall respectively, 
$h=L/N_\iin$ be the resolution mesh size of the body, 
and $d$ be the minimum initial distance from body to wall. 
To investigate the shape of eroding body when it is close to wall, 
we set $r=0.4$, $N_\iin=256$, and $N_\out=1024$ 
with respect to three different $d=h, h/2$, and $ h/10$.

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.45 \textwidth]{./figs/velocity_loc}
\includegraphics[width = 0.45 \textwidth]{./figs/tort_local}\\

\includegraphics[width = 0.45 \textwidth]{./figs/tortU_local}
\includegraphics[width = 0.45 \textwidth]{./figs/uminDumax}

\caption{The tortuosity of the 20 nearly touching bodies}
\end{center}
\end{figure}

@@

\subsection{100 bodies}
{\color{red}
This case is 100 bodies in a Hagen-Poiseuille flow.
}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_50}
\caption{\label{fig:Eroding100vort} Erosion of 100 bodies with the fixed-pressure-drop condition. The color is the vorticity of fluid. In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $}
\end{center}
\end{figure}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.8\textwidth]{./figs/100b_t100tracer}
\caption{\label{fig:Eroding100tracer} The trajectories of 200 tracers in the fluid with 100 bodies}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{s:conclusions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
